Architectures and Open pNets

### 2018-05-15 2016-Weak-FH-Bisim/WeakBisim.tex

Rabea
\begin{itemize}
\item uniformiser p et P pour les pnets
\item relectures
\end{itemize}
=== en parallele

@@

  For any pNet p, let $\Leaves(p) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
  the set of pLTS at its leaves,
  then $States(p) = \{\triangleleft s_i^{i\in L}
  \triangleright| \forall i\in L. s_i \in S_i\}$.
A pLTS being its own single leave:
  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.

The initial state is defined as:
$InitState(p) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
\end{definition}

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\begin{array}{l}\Pred_{\symb{sv}}(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
{\alpha'} 
{e_b}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha)\Leftrightarrow \\~\qquad\qquad%\bigg(
%
%\exists {(\alpha'_i)}^{i\in I},
%{(\beta'_j)}^{j\in J},v'.\, SV=
%\\~~\land
\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
\alpha=\alpha' 
\land e_b
\end{array} 
%\bigg)
\]

@@

\begin{definition}[Operational semantics of open pNets]
	\label{def:operationalSemantics}
	The semantics of a pNet $p$ is an open automaton $A = 
	<Holes(p),States(p),InitState(p),
	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\begin{itemize}
%		\item $J$ is the set of holes: $Holes(p)= J$. 
		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\end{itemize}

@@

       	\begin{mathpar}

@@

       	\begin{mathpar}

@@

       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \beta_{jpx}=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$\\.

>>>>

Rabea
\begin{itemize}
\item uniformiser p et P pour les pnets \RAB{Done for definitions 6 and 7. We will chek for lemmas 1 and 2}
\item relectures
\end{itemize}
=== en parallele

@@

  For any pNet: \pNet, let $\Leaves(\pNet) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
  the set of pLTS at its leaves,
  then $States(\pNet) = \{\triangleleft s_i^{i\in L}
  \triangleright| \forall i\in L. s_i \in S_i\}$.
A pLTS being its own single leave:
  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.

The initial state is defined as:
$InitState(\pNet) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
\end{definition}

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\begin{array}{l}\Pred_{\symb{sv}} \Big(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
{\alpha'} 
{e_b}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha\Big)\Leftrightarrow \\~\qquad\qquad%\bigg(
%
%\exists {(\alpha'_i)}^{i\in I},
%{(\beta'_j)}^{j\in J},v'.\, SV=
%\\~~\land
\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
\alpha=\alpha' 
\land e_b
\end{array} 
%\bigg)
\]

@@

\begin{definition}[Operational semantics of open pNets]
	\label{def:operationalSemantics}
	The semantics of a pNet $\pNet$ is an open automaton $A\!= 
	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),
	\mathcal{T}\!\!>$ where $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\begin{itemize}
%		\item $J$ is the set of holes: $Holes(p)= J$. 
		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
%	\end{itemize}

@@

       	\begin{mathpar} \qquad (*)

@@

       	\begin{mathpar} \qquad (**)

@@

       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \beta_{jpx}=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\

### 2018-05-15 2018-Arch-pNets/arch-pNets.tex

\begin{definition}[Components]
  \label{defn:component}
  A \emph{component} is a tuple $(Q, q^0, V, \val{0}{}, P,
  \export, \goesto{})$, where
  \begin{itemize}
  \item $Q$ is a set of \emph{states}, with $q^0 \in Q$ the
    \emph{initial state}, 
  \item $V$ is a set of \emph{component variables},
  \item $\val{0}{} : V \rightarrow \data$ is an \emph{initial
    valuation} of the component variables, 
  \item $P$ is a set of \emph{ports}, with
    \noteSB{Added this}\hl{$\export : P \rightarrow 2^V$ 
    the \emph{export function},}
  \item $\goesto{}\, \subseteq
    Q \times 2^P \times \guards{V} \times \exprs{V} \times Q$
%
    is a \emph{transition relation}, with transitions
    labelled by \emph{interactions}, \ie triples consisting of a non-empty set of ports
    $\emptyset \neq a \subseteq P$, a monotonic Boolean \emph{guard} $g \in
    \guards{V}$ and a monotonic \emph{update expression} \todoSB{$e \rightarrow u$}\hl{$e \in
    \exprs{V}$}.
  \end{itemize}
%
  We call the triple $(V,P, \export)$ the \emph{interface} of the
  component.\,\footnote{%
%
  In practice, component variables are split in two sub-sets:
  local and exported variables.  Only exported variables belong
  to the component interface and can be used for the interactions
  with other components (see \defn{im}).  However, in the context
  of this paper we can simplify by omitting this separation.
%
  }
%
  Notations $q \goesto{a, g, e} q'$ and $q \goesto{a, g, e}$ are as usual;
  for a component $B$, we denote $Q_B$, $q^0_B$, $V_B$, $\val{0}{B}$, $P_B$,
  and $\export[B]$ the corresponding constituents of $B$.  We will
  skip the index on the transition relations $\goesto{}$, since it
  is always clear from the context.
\end{definition}

@@

\begin{definition}[Interaction model]
  \label{defn:im}
  Consider a finite set of component interfaces $(V_i, P_i,
  \export[i])^{i \in I}$, such that all $P_i$ and all $V_i$ are
  pairwise disjoint, \ie $\forall i \neq j,\ P_i \cap P_j = V_i \cap
  V_j = \emptyset$.  Let $P = \bigcup_{i \in I} P_i$, $V = \bigcup_{i
    \in I} V_i$ and $\export : P \rightarrow 2^V$ such that, for any
  $p \in P_i$, $\export(p) = \export[i](p)$.
%
  For a set of ports $a \subseteq P$, we denote $\supp{a}
  \bydef{=} \setdef{i \in I}{a \cap P_i \neq \emptyset}$ the
  \emph{support} of $a$.
  %% \noteSB{Updated this}\hl{and $V_a \bydef{=} \bigcup_{i \in
  %%   \supp{a}} \export[i](a \cap P_i)$ the set of component
  %% variables exported through $a$.}

@@

Connectors are hierarchical, tree-like structures with component ports
at the leaves.  They define sets of \emph{interactions}, based on the
attributes of the connected ports~\cite{BliSif08-acp-tc}, which may be
either \emph{trigger} (triangles in Fig.~\ref{schema:ArchFailure:BIP})
or \emph{synchron} (bullets in Fig.~\ref{schema:ArchFailure:BIP}).
%
If all sub-connectors of a connector are synchrons, then an
interaction may be executed by the connector only if each subconnector
can contribute.
%
If at least one of the sub-connectors is a trigger, then any
interaction consisting of contributions of any set of sub-connectors,
\emph{involving at least one of the triggers}, can be executed.
%
For instance, the two ports $\NameTimer.\PortStart$ and
$\NameCtrl.\PortFail$ are always synchronised, since they belong to
the same binary sub-connector, where they are both synchrons.  In
particular, this means that whenever the transition $\cstate{0}
\goesto{\PortFail} \cstate{1}$ is fired, so is the transition
$\tstate{0} \goesto{\PortStart, \TimerInit[]} \tstate{1}$,
initialising the timer.  The binary connector $\NameTimer.\PortStart
\bullet\!\!\!-\!\!\!-\!\!\!\bullet \NameCtrl.\PortFail$ is a
sub-connector of a hierarchical connector, where the port
$\NameOprnd.\PortFail$ is a trigger.  Thus, the above interaction can
only happen together with $\NameOprnd.\PortFail$, forming a
ternary interaction.  On the contrary, being a trigger, the port
$\NameOprnd.\PortFail$ can fire alone, forming a singleton
interaction.  The composition semantics of BIP systems consists in
firing exactly one interaction, enabled through at least one of the
top-level connectors, at each execution round.

>>>>

\begin{definition}[Components]
  \label{defn:component}
  A \emph{component} is a tuple $(Q, q^0, V, \val{0}{}, P,
  \export, \goesto{})$, where
  \begin{itemize}
  \item $Q$ is a set of \emph{states}, with $q^0 \in Q$ the
    \emph{initial state}, 
  \item $V$ is a set of \emph{component variables},
  \item $\val{0}{} : V \rightarrow \data$ is an \emph{initial
    valuation} of the component variables, 
  \item $P$ is a set of \emph{ports}, with
    \noteSB{Added this}\hl{$\export : P \rightarrow 2^V$ 
    the \emph{set of variables exported by each port},}
  \item $\goesto{}\, \subseteq
    Q \times 2^P \times \guards{V} \times \exprs{V} \times Q$
%
    is a \emph{transition relation}, with transitions
    labelled by \emph{interactions}, \ie triples consisting of a non-empty set of ports
    $\emptyset \neq a \subseteq P$, a monotonic Boolean \emph{guard} $g \in
    \guards{V}$ and a monotonic \emph{update expression} \todoSB{$e \rightarrow u$}\hl{$e \in
    \exprs{V}$}.
  \end{itemize}
%
  We call the triple $(V,P, \export)$ the \emph{interface} of the
  component.\,\footnote{%
%
  In practice, component variables are split in two sub-sets:
  local and exported variables.  Only exported variables belong
  to the component interface and can be used for the interactions
  with other components (see \defn{im}).  However, in the context
  of this paper we can simplify by omitting this separation.
%
  }
%
  Notations $q \goesto{a, g, e} q'$ and $q \goesto{a, g, e}$ are as usual;
  for a component $B$, we denote $Q_B$, $q^0_B$, $V_B$, $\val{0}{B}$, $P_B$,
  and $\export[B]$ the corresponding constituents of $B$.  We will
  skip the index on the transition relations $\goesto{}$, since it
  is always clear from the context.
\end{definition}

@@

\begin{definition}[Interaction model]
  \label{defn:im}
  Consider a finite set of component interfaces $(V_i, P_i,
  \export[i])^{i \in I}$, such that all $P_i$ and all $V_i$ are
  pairwise disjoint, \ie $\forall i \neq j,\ P_i \cap P_j = V_i \cap
  V_j = \emptyset$.  Let $P = \bigcup_{i \in I} P_i$, $V = \bigcup_{i
    \in I} V_i$ and $\export : P \rightarrow 2^V$ such that, for any
  $p \in P_i$, $\export(p) = \export[i](p)$. \noteLH{supp should go outside the definition}
%
  For a set of ports $a \subseteq P$, we denote $\supp{a}
  \bydef{=} \setdef{i \in I}{a \cap P_i \neq \emptyset}$ the
  \emph{support} of $a$.
  %% \noteSB{Updated this}\hl{and $V_a \bydef{=} \bigcup_{i \in
  %%   \supp{a}} \export[i](a \cap P_i)$ the set of component
  %% variables exported through $a$.}

@@

\noteLH{Ludo ou simon: essayer de remonter la description generique en debut de section}
Connectors are hierarchical, tree-like structures with component ports
at the leaves.  They define sets of \emph{interactions}, based on the
attributes of the connected ports~\cite{BliSif08-acp-tc}, which may be
either \emph{trigger} (triangles in Fig.~\ref{schema:ArchFailure:BIP})
or \emph{synchron} (bullets in Fig.~\ref{schema:ArchFailure:BIP}).
%
If all sub-connectors of a connector are synchrons, then an
interaction may be executed by the connector only if each subconnector
can contribute.
%
If at least one of the sub-connectors is a trigger, then any
interaction consisting of contributions of any set of sub-connectors,
\emph{involving at least one of the triggers}, can be executed.
%
For instance, the two ports $\NameTimer.\PortStart$ and
$\NameCtrl.\PortFail$ are always synchronised, since they belong to
the same binary sub-connector, where they are both synchrons.  In
particular, this means that whenever the transition $\cstate{0}
\goesto{\PortFail} \cstate{1}$ is fired, so is the transition
$\tstate{0} \goesto{\PortStart, \TimerInit[]} \tstate{1}$,
initialising the timer.  The binary connector $\NameTimer.\PortStart
\bullet\!\!\!-\!\!\!-\!\!\!\bullet \NameCtrl.\PortFail$ is a
sub-connector of a hierarchical connector, where the port
$\NameOprnd.\PortFail$ is a trigger.  Thus, the above interaction can
only happen together with $\NameOprnd.\PortFail$, forming a
ternary interaction.  On the contrary, being a trigger, the port
$\NameOprnd.\PortFail$ can fire alone, forming a singleton
interaction.  The composition semantics of BIP systems consists in
firing exactly one interaction, enabled through at least one of the
top-level connectors, at each execution round.
